\documentclass[sigconf]{acmart}
% \acmSubmissionID{736}


\usepackage{booktabs} % For formal tables
\usepackage{url}
\usepackage{hyperref}
\usepackage{balance}
% Copyright
% \setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}



% \copyrightyear{2016}


% \acmArticle{4}
% \acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
% \editor{Jennifer B. Sartor}
% \editor{Theo D'Hondt}
% \editor{Wolfgang De Meuter}



\begin{document}

\title{Deep Cross Modal Learning for Caricature Verification and Identification(CaVINet)}

\author{Jatin Garg}\authornote{Authors with equal contribution}
\affiliation{
    \institution{Indian Institute of Technology Ropar}
}
 \email{2014csb1017@iitrpr.ac.in}
 
\author{Skand Vishwanath Peri}\authornotemark[1]
\affiliation{
    \institution{Indian Institute of Technology Ropar}
}
  \email{pvskand@gmail.com}
  
\author{Himanshu Tolani}\authornotemark[1]
\affiliation{
    \institution{Indian Institute of Technology Ropar}
}
  \email{2014csb1015@iitrpr.ac.in}
  
\author{Narayanan C Krishnan}
\affiliation{
    \institution{Indian Institute of Technology Ropar}
}
  \email{ckn@iitrpr.ac.in}



\subtitle{\href{https://lsaiml.github.io/CaVINet/}{\texttt{\textcolor{red}{https://lsaiml.github.io/CaVINet/}}}}



% \textcolor{blue}{\Large \url{https://lsaiml.github.io/CaVINet/}}
% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Jatin Garg, Skand V Peri, Himanshu Tolani, and Narayanan C Krishnan}



\begin{abstract}
Learning from different modalities is a challenging task. In this paper, we look at the challenging problem of cross modal face verification and recognition between caricature and visual image modalities. Caricature have exaggerations of facial features of a person. Due to the significant variations in the caricatures, building vision models for recognizing and verifying data from this modality is an extremely challenging task. Visual images with significantly lesser amount of distortions can act as a bridge for the analysis of caricature modality. We introduce a publicly available large \textbf{Ca}ricature-\textbf{VI}sual  dataset [CaVI] with images from both the modalities that captures the rich variations in the caricature of an identity. This paper presents the first cross modal architecture that handles extreme distortions of caricatures using a deep learning network that learns similar representations across the modalities. We use two convolutional networks along with transformations that are subjected to orthogonality constraints to capture the shared and modality specific representations. In contrast to prior research, our approach neither depends on manually extracted facial landmarks for learning the representations, nor on the identities of the person for performing verification. The learned shared representation achieves 91\% accuracy for verifying unseen images and 75\% accuracy on unseen identities. Further, recognizing the identity in the image by knowledge transfer using a combination of shared and modality specific representations, resulted in an unprecedented performance of 85\% rank-1 accuracy for caricatures and 95\% rank-1 accuracy for visual images.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
% \begin{CCSXML}
% <ccs2012>
%  <concept>
%   <concept_id>10010520.10010553.10010562</concept_id>
%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%   <concept_significance>500</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010575.10010755</concept_id>
%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%   <concept_significance>300</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10010520.10010553.10010554</concept_id>
%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
%  <concept>
%   <concept_id>10003033.10003083.10003095</concept_id>
%   <concept_desc>Networks~Network reliability</concept_desc>
%   <concept_significance>100</concept_significance>
%  </concept>
% </ccs2012>  
% \end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}


\keywords{Cross-modal recognition, Caricature verification and recognition, deep learning}
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmcopyright}
\acmConference[MM '18]{2018 ACM Multimedia Conference}{October 22-26, 2018}{Seoul, Republic of Korea}

\acmPrice{15.00}
\acmDOI{10.1145/3240508.3240658}
\acmISBN{978-1-4503-5665-7/18/10}
\settopmatter{printacmref=true} 
\maketitle
\fancyhead{}
\input{cavinet_body}

\bibliographystyle{ACM-Reference-Format}
\balance
\bibliography{cavinet} 

\end{document}
